Almost compatible functions and infinite length games

### 2015-12-11 articles/almost-compatible-functions-and-topological-games/article.tex
partial edits of omega_2 cohen reals proof

  \begin{lemma}[\cite{MR597342}]
    Assume that $G\subset \operatorname{Fn}(\omega_2,2)$ is a generic filter,
    and let $\mu\in \omega_2$. Then the final model $V[G]$ can be
    regarded as forcing  with $\operatorname{Fn}(\omega_2\setminus \mu,
    2)$ over the model $V[G_\mu]$.
    In addition, for each $\operatorname{Fn}(\omega_2,2)$-name $\dot A$
    for $A\subseteq\omega$ (abusing notation and letting \(n\) represent
    its own $\operatorname{Fn}(\omega_2,2)$-name and
    $\operatorname{Fn}(\omega_2\setminus \mu, 2)$-name),
    there is a canonical name $\dot A(G_\mu)$ where,
    $$\dot A(G_\mu) = \{ (n,p\restriction [\mu,\omega_2))  :
    (n,p)\in \dot A\ \ \mbox{and} \ \ p\restriction \mu\in G_\mu\}$$
    and the valuation of $\dot A(G_\mu)$ by the tail
    of the generic, $G_{\omega_2\setminus \mu}$, is the same as
    the valuation of $\dot A$ by the full generic.
  \end{lemma}

 \begin{lemma}[\cite{MR597342}]
    Assume that \(G\subset \operatorname{Fn}(\omega_2,2)\) is a generic filter,
    and let \(\mu\in \omega_2\). Then the final model \(V[G]\) can be
    regarded as forcing  with \(\operatorname{Fn}(\omega_2\setminus \mu,
    2)\) over the model \(V[G_\mu]\).
    In addition, for each \(\operatorname{Fn}(\omega_2,2)\)-name \(\dot A\)
    for \(A\subseteq\omega\) (abusing notation and letting \(n\) represent
    its own \(\operatorname{Fn}(\omega_2,2)\)-name and
    \(\operatorname{Fn}(\omega_2\setminus \mu, 2)\)-name),
    there is a canonical name \(\dot A(G_\mu)\) where,
    \[\dot A(G_\mu) = \{ (n,p\restriction [\mu,\omega_2))  :
    (n,p)\in \dot A\ \ \mbox{and} \ \ p\restriction \mu\in G_\mu\}\]
    and the valuation of \(\dot A(G_\mu)\) by the tail
    of the generic, \(G_{\omega_2\setminus \mu}\), is the same as
    the valuation of \(\dot A\) by the full generic.
  \end{lemma}

@@

  \begin{proof}
    The forcing poset is \(\operatorname{Fn}(\omega_2, 2)\).
    Let \(\{ \dot f_{A} : A\in [\omega_2]^\omega\}\) be a family of
    names such that \(f_{A}\) is a one-to-one function from \(A\) into
    \(\omega\) in the ground model. Let \(M\) be an elementary submodel
    of the universe such that
    \(|M|=\omega_1 =\mathfrak c\) and \(M^\omega\subset M\).

    Let \(\lambda = M\cap \omega_2=\sup(M\cap\omega_2)\).
    Consider the name
    \[
      \dot f_{[\lambda,\lambda+\omega)}
        =
      \{
        ( (\lambda+k,m), p)
      :
        p\in \mathop{Fn}(\omega_2,2);k,m\in \omega
      \}
    \]
    This is (almost) equivalent to
             saying
             that \(p\) forces that \(\dot f_{[\lambda,\lambda+\omega)}(\lambda+k) =
             m\). We don't take all such \(p\), in fact for each \(k,m\) it is enough
            to take a
             countable set of such \(p\) to get an equivalent name
             (Kunen calls it a nice name if we take, for each \(k,m\) an
            antichain that is maximal among such conditions).
            Given any such name \(\dot f\), let \(\operatorname{supp}(\dot f)\)
            denote the union of the domains of conditions \(p\) appearing in the
            name.

             Also let \(Y\) equal \(\operatorname{supp}(\dot
             f_{[\lambda,\lambda+\omega)})\setminus \lambda\).
             Let \(\delta\) denote the order type of
             \(Y\) and let the 2-parameter notation
             \(\varphi_{\mu,\lambda}\) be the order-preserving function from
            \(\mu\cup Y\) onto  the ordinal \(\mu+\delta\).  This lifts canonically to
            an order-preserving bijection \(\varphi_{\mu,\lambda}:
            \operatorname{Fn}(\mu\cup Y,2) \mapsto
            \operatorname{Fn}(\mu+\delta,2)\).
            Similarly, we make sense of the name
             \(\varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})\), call it \(F_M\).
            Here simply, for each tuple \((~(k,m)~, p)\in \dot
            f_{[\lambda,\lambda+\omega)}\),
             we have that \((~(k,m)~,\varphi_{\mu,\lambda}(p))\) is in \(F_M\).
            Again, let \(\varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})\)
            be interpreted in the above sense as giving \(F_M\) (which is an element
            of \(M\)).  Note that we do not regard \(\delta\) as fixed here, but
            rather simply depending on the \(\operatorname{supp}(\dot
            f_{[\lambda,\lambda+\omega)})\) described above. Other values
            replacing \(\lambda>\mu\) will result in their own set \(Y\)
            and canonical map \(\varphi_{\mu,\lambda}\); but one thing we do have to
            assume (or arrange) for other values \(\alpha\) replacing \(\lambda\)
            is that \(\operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})\)
            intersected with
            \(\alpha\) is contained in \(\mu\).

>>>>

 \begin{lemma}[\cite{MR597342}]
    Assume that \(G\subset \operatorname{Fn}(\omega_2,2)\) is a generic filter,
    and let \(\mu\in \omega_2\). Then the final model \(V[G]\) can be
    regarded as forcing with
    \(\operatorname{Fn}(\omega_2\setminus \mu, 2)\) over the model \(V[G_\mu]\).
    Let \(\dot n,\ddot n\) be a
    \(\operatorname{Fn}(\omega_2,2)\)-,
    \(\operatorname{Fn}(\omega_2\setminus\mu,2)\)-name respectively for each
    \(n<\omega\). Then for each \(\operatorname{Fn}(\omega_2,2)\)-name \(\dot A\)
    for \(A\subseteq\omega\), there is a canonical
    \(\operatorname{Fn}(\omega_2\setminus \mu, 2)\)-name
    \[
      \ddot A
        =
      \{
        (\ddot n,p\rest [\mu,\omega_2))
      :
        (\dot n,p)\in \dot A
      \}
    \]
    which satisfies
    \(
      A
        =
      \operatorname{val}(\dot A,G)
        =
      \operatorname{val}(\ddot A,G_\mu)
    \).
  \end{lemma}

@@

  \begin{proof}
    The forcing poset is \(\mb P=\operatorname{Fn}(\omega_2, 2)\).
    Let \(\{ \dot f_{A} : A\in [\omega_2]^\omega\}\) be a family of
    \(\mb P\)-names such that \(f_{A}\) is a one-to-one function from \(A\) into
    \(\omega\) in the ground model. Let \(M\) be an elementary submodel
    of the universe containing \(\mb P\) such that
    \(|M|=\omega_1 =\mathfrak c\) and \(M^\omega\subset M\).

    Let \(\lambda\) be the ordinal \(M\cap \omega_2\).
    We may assume
    \(
      \dot f_{[\lambda,\lambda+\omega)}
        =
      \{
        ((\lambda+k_p,m_p)^\cdot, p)
      :
        p\in C
      \}
    \)
    for some countable \(C\subseteq\operatorname{Fn}(\omega_2,\omega)\).
    Let
    \(
      \operatorname{supp}(\dot f_{[\lambda,\lambda+\omega)})
        =
      \bigcup_{p\in C}\operatorname{dom} p
    \).

    Let \(\delta_\lambda\) denote the order type of
    \(\operatorname{supp}(\dot f_{[\lambda,\lambda+\omega)})\setminus \lambda\),
    and for \(\mu\leq\lambda\) let \(\varphi_{\mu,\lambda}'\) be the
    order-preserving bijection from
    \(
      \mu\cup
      \left(\operatorname{supp}(\dot f_{[\lambda,\lambda+\omega)})
        \setminus
      \lambda\right)
    \)
    onto the ordinal \(\mu+\delta_\lambda\).
    This lifts canonically to an order-preserving bijection
    \(
      \varphi_{\mu,\lambda}
        :
      \operatorname{Fn}(\mu\cup Y,2)
        \to
      \operatorname{Fn}(\mu+\delta,2)
    \).

    Consider the \(\mb P\)-name
    \(
      F_M
        =
      \{
        ((\lambda+k_p,m_p)^\cdot,\varphi_{\mu,\lambda}(p))
      :
        ((\lambda+k_p,m_p)^\cdot,p)\in\dot f_A
      \}
    \).

    % Other values
    %         replacing \(\lambda>\mu\) will result in their own set \(Y\)
    %         and canonical map \(\varphi_{\mu,\lambda}\); but one thing we do have to
    %         assume (or arrange) for other values \(\alpha\) replacing \(\lambda\)
    %         is that \(\operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})\)
    %         intersected with
    %         \(\alpha\) is contained in \(\mu\).
